---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# nycha

<!-- badges: start -->
<!-- badges: end -->

Spatial and tabular data about the New York City Housing Authority
(NYCHA), including public housing development boundaries, residential
addresses, the NYCHA Development Data Book, housing maintenance code
violations on NYCHA properties, community facilities, service centers,
and aggregate resident statistics.

## Installation

```r
remotes::install_github("kjhealy/nycha")
```

## Load

```{r load, message = FALSE}
library(nycha)
library(tidyverse)
library(sf)
```

## What's included

```{r objects}
nyc_developments_sf
nyc_addresses_df
nyc_violations_df
nyc_community_facilities_df
nyc_facilities_df
nyc_development_data_df
nyc_resident_summary_df
```

## Example: total apartments and population by borough

```{r summary}
nyc_development_data_df |>
  summarise(
    developments = n(),
    apartments = sum(total_number_of_apartments, na.rm = TRUE),
    population = sum(total_population, na.rm = TRUE),
    .by = borough
  ) |>
  arrange(desc(apartments))
```

## Example: map of NYCHA developments

```{r map, fig.alt = "Map of New York City showing the locations and footprints of NYCHA public housing developments coloured by borough."}
ggplot(nyc_developments_sf) +
  geom_sf(aes(fill = borough), colour = NA) +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "NYCHA public housing developments",
    fill = NULL
  ) +
  theme_minimal()
```
